Population Inference of Eccentric Binary Black Holes

### 2023-05-09 paper/paper.tex
Added HBM and inference subsection in method section

>>>>

\subsection{Hierarchical Bayesian Modeling}
\begin{itemize}
    \item We have N discrete detection.
    \item each detection has data $d_1,d_2,d_3,...,d_N$
    \item each data point $d_N$ has properties denoted by $\lambda_1,\lambda_2,...,\lambda_i$
    \item  $ \lambda_i$ are parameters such as mass, spin, eccentricity, and location.
    \item Each parameter has its uncertainty.
    \item This uncertainty is described by the probability of the data given the parameter value. We call it the likelihood function of one single event. $\mathcal{L}(\lambda) = p(d|\lambda)$
    \item the waveform gives the parameter value.
    \item waveform is a mathematical function.
    \item Once you have a likelihood function, you can use prior( usually it's uniform: which gives equal probability to each event) to find the posterior. $p(\lambda|d) \propto p(d|\lambda) p(\lambda)$

\end{itemize}

\subsection{Population Inference}

\begin{itemize}
    \item We have the parameter estimation from RIFT or any other method. It will give us a distribution for each parameter, and we may take the mean value of it.
    \item Our first task is to find the likelihood function for the population parameters: such as mass and eccentricity.
    \item We denote population parameters with \\ $\Lambda \equiv  (\alpha, \mathcal{R}, m_{min}, m_{max}, e)$.
    \item uncertainty in $\Lambda$ is a likelihood which can be written as $\mathcal{L}(\Lambda)\equiv p(d_1,d_2,d_3,...,d_N|\Lambda)$
    \item By applying the Bayes theorem, we can turn above likelihood into posterior probability of a parameter.
    $p(\Lambda|d_1,d_2,d_3,...,d_N)= \frac{p(\Lambda)*p(d_1,d_2,d_3,...,d_N|\Lambda)}{p(d_1,d_2,d_3,...,d_N)}$
    \item where $p(\Lambda|d_1,d_2,d_3,...,d_N)$ is posterior, $p(\Lambda)$ is prior, $p(d_1,d_2,d_3,...,d_N)$ is normalization/evidence, and $p(d_1,d_2,d_3,...,d_N|\Lambda)$ is likelihood.
    \item We will use inhomogeneous Poisson Process scaled by rate $\mathcal{R} = \frac{dN}{dtdV_c}$ and parameterize by $\Lambda$ to find the likelihood  $\mathcal{L}(\mathcal{R},\Lambda)\equiv p(D|\mathcal{R},\Lambda)$ of an astrophysical population given the merger rate and parameter $\Lambda$. 
    {\color{red}I think these values of $\Lambda$ are provided by the power law model}. \\
    $\mathcal{L}(\mathcal{R},\Lambda) \propto e^{-\mu(\mathcal{R},\Lambda)}\prod_{n=1}^N\int d\lambda l_n(\lambda) \mathcal{R} p(\lambda|\Lambda)$
    \item where $\mu(\mathcal{R},\Lambda)$ are the expected number of detections under the given population parametrization $\Lambda$ with overall rate $\mathcal{R}$. $l_n(\lambda)=p(d_n|\lambda)$ is the likelihood of the data $d_n$ given binary parameter.
    \item now we can find the posterior by Baye's theorem. \\
    $p(\mathcal{R,\Lambda})\propto p(\mathcal{R},\Lambda) * \mathcal{L}(\mathcal{R},\Lambda)$
    \item calculation of this posterior is computationally expensive, therefore, we will use MCMC method to find the posterior distribution.

\end{itemize}
